### 2020-05-27 writeup/intro.tex

\begin{abstract}
When does multi-task and transfer learning outperform single-task learning? In this paper, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff. In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators. A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.

	We consider multi-task and transfer learning approaches to better understand when we should expect them to outperform single-task learning.
	We study the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture.
	For the setting of linear regressions in the high-dimensional regime, we provide sharp bias-variance tradeoffs for multi-task and transfer learning estimators.
	A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
\end{abstract}

>>>>

\begin{abstract}
When does multi-task and transfer learning outperform single-task learning?
In this paper, we address this question by studying the test performance of predicting a particular task given multiple tasks using a commonly used hard parameter sharing architecture, in terms of bais-variance tradeoff.
In the case of high-dimensional linear regression, we provide a sharp analysis of the bias-variance tradeoff for multi-task and transfer learning estimators.
A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$ in the setting of two tasks.
	Based on the theory, we provide more precise interpretations of many empirical phenomena in multi-task and transfer learning.
	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
\end{abstract}
